Redundant calibration as a complex optimization problem

### 2016-12-05 paper.tex
abstract started

\begin{abstract}
Traditionally redundant calibration is implemented via a layered algorithmic pipeline, i.e. a basic firstcal is performed, followed by LOGCAL and LINCAL.  We first show
that LINCAL is effectively the non-linear least-squares Gauss-Newton algorithm. An easy way to reduce the number of layers that are currently used would therefore be to employ the Levenberg-Marquardt algorithm instead. We further show that instead of splitting our calibration problem into its phase and amplitude components,
which is the avenue taken by LINCAL, we can treat the complex unknown parameters and their complex conjugates as separate unknowns instead.

>>>>

\begin{abstract}
Traditionally redundant calibration is implemented via a layered algorithmic pipeline, i.e. a basic firstcal is performed, followed by LOGCAL and LINCAL.  We first show
that LINCAL is effectively the non-linear least-squares Gauss-Newton algorithm. An easy way to reduce the number of layers that are currently used would therefore be to employ the Levenberg-Marquardt algorithm instead. 
We further show that instead of splitting our calibration problem into its phase and amplitude components,
which is the avenue taken by LINCAL, we can treat the complex unknown parameters and their complex conjugates as separate unknowns instead. In the latter approach 
we use Wirtinger derivatives instead of the classical definition of differentiation. Lastly, we compare two previously proposed methods, to increase the speed of redundant 
calibration, with each other. The two approaches we investigate is the alternating direction implicit method and the preconditioned conjugate gradient method. We specifically use 
the Wirtinger framework in this paper, instead of the phase amplitude approach, as it is easy to show that the alternating direction implicit method is simply a special case
